Lattices of acyclic pipe dreams

### 2023-03-17 acyclicFacets/draft/latticePipeDreams.tex
added Remark 5.29 about connection between our sweeping algorithm and the algorithm of Jahn-Stump

We now extend the sweeping algorithm of \cref{subsec:sweepingAlgorithm} to construct, from a linear extension $\pi \in \linearExtensions(Q,\omega)$, the unique acyclic facet~$I$ such that $\pi \in \linearExtensions(I)$.
We note that this algorithm was independently described in~\cite{JahnStump}.

@@

We first need to argue that the algorithm terminates, that is, that any position $j$ falls into one of the four cases above.

>>>>

We now extend the sweeping algorithm of \cref{subsec:sweepingAlgorithm} to construct, from a linear extension $\pi \in \linearExtensions(Q,\omega)$, the unique acyclic facet~$I$ such that $\pi \in \linearExtensions(I)$.
We note that this algorithm is related to an algorithm that was independently described in~\cite{JahnStump}, see Remark~\ref{rem_sweepJahnStump}.

@@

\begin{remark}\label{rem_sweepJahnStump}
In~\cite[Section~3.3]{JahnStump}, Jahn and Stump describe an algorithm to compute the $f$-antigreedy facet of a subword complex $\subwordComplex(Q,\omega)$ associated to a linear functional $f$.  
The output of our algorithm coincides with the output of Jahn-Stump's algorithm whenever $f$ is positive on~$\pi(\Phi^+)$ and negative on $\pi(\Phi^-)$, see~\cite[Proposition~4.12]{JahnStump}.
Also, compare Proposition~\ref{prop:sweeping}~\eqref{item:sweeping1} with~\cite[Theorem~3.17 (a)]{JahnStump},
and Proposition~\ref{prop:sweeping}~\eqref{item:sweeping2} with the second part of~\cite[Proposition~4.12]{JahnStump}.

Although the algorithm presented in~\cite{JahnStump} is more general, our sweeping algorithm is more direct when computing the output for the input $\pi$, since we skip the step of translating the conditions on the sign of $f(\rootFunction{I^j}{j})$ in Jahn-Stump's algorithm. We remark that these two algorithms were developed independently, while approaching different problems. This highlights the relevance of the sweeping algorithm.  
\end{remark}

In order to prove Proposition~\ref{prop:sweeping}, we first need to argue that the algorithm terminates, that is, that any position $j$ falls into one of the four cases above.
